Predicting Covid Data

### 2022-12-05 chien_sim.Rmd
test

```{r, echo=FALSE, message=FALSE, warning=FALSE, results=FALSE}
#output
print(mean(flex_fa))
print(sd(flex_fa))
print(mean(flex_ca))
print(sd(flex_ca))
```

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE, results=FALSE}
#output
print(mean(flex_fa))

print(sd(flex_fa))
print(mean(flex_ca))
print(sd(flex_ca))
```
